Genome-wide changes in expression during inflorescence architecture development

### 2015-08-17 ms.Rmd
Flip, capitalization error in shuffle script was excluding rRNA regions. start again

# Results

@@

![`r I(pasteLabel("Figure", figCount, "f_lmdFigure"))`](data/lmdFigure.pdf)

@@

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.height=6.3, cache = TRUE}
print(f_mfuzzClusters)
```

@@

Hypergeometric tests were performed for each cluster that contained more than one member of a particular TF family to calculate the probability of observing the corresponding

+ **Figure**: Gene expression clusters
+ GO enrichment? NO! z-score enrichment of transcription factor genes per cluster. Use dhyper in R (see http://jura.wi.mit.edu/bio/education/hot_topics/enrichment/Gene_list_enrichment_Mar10.pdf or http://stats.stackexchange.com/a/16259)
+ Clusters including 'known' genes

@@

# Discussion

@@

`r I(pasteLabel("Figure", figCount, "f_mfuzzClusters"))`
**Common patterns of expression in the meristem samples.**

Fuzzy *c*-means clustering of normalised, variance-stabilised read counts was used to recover `r capwords(as.character(english::english(c)))` common patterns of expression. Each line describes the expression pattern of one gene, with the gene's membership to the cluster mapped to the colour of the line. The core values for each cluster are plotted in black.

>>>>

# Results and Discussion

@@

To investigate gene expression during inflorescence development, LASER microdissection (LMD) was used to collect meristematic tissues from the rachis meristem (RM), primary branch meristem (PBM), elongating primary branch meristem and secondary branch meristem (ePBM/SBM) and spikelet meristem (SM) (`r I(pasteLabel("Figure", figCount, "f_lmdFigure"))`). RNA from the meristem samples was isolated, amplified and used for the production of a sequencing library. **Details of the procedure, yield, etc.**.

<a id="f_lmdFigure"></a>
![](data/lmdFigure.pdf)

@@

<a id="f_mfuzzClusters"></a>
```{r f_mfuzzClusters, fig.height=6.3}
print(f_mfuzzClusters)
```

@@

+ Clusters including 'known' genes

@@

@@

`r I(pasteLabel("Figure", figCount, "f_lmdFigure"))`
**LASER microdissection of meristem samples in the early stages of inflorescences development.** Samples were collected from the rachis meristem (**a** and **e**), the primary branch meristem (**b** and **f**), the elongating primary branch meristem and secondary branch meristem (**c** and **g**) and the spikelet meristem (**d** and **h**). Images show the samples before (**a**–**d**) and after (**e**–**h**) dissection.

`r I(pasteLabel("Figure", figCount, "f_mfuzzClusters"))`
**Common patterns of expression in the meristem samples.** Fuzzy *c*-means clustering of normalised, variance-stabilised read counts was used to recover `r capwords(as.character(english::english(c)))` common patterns of expression. Each line describes the expression pattern of one gene, with the gene's membership to the cluster mapped to the colour of the line. The core values for each cluster are plotted in black.
